Cartograms with Rivers

### 2023-03-23 paper/section/evaluation.tex
draft: review 3

    {
        \begin{figure}[tb!]
            \centering
            \includegraphics[width=\columnwidth,keepaspectratio]{figure/evaluation/task.png}
            \caption{A sample location task for participants. The left shows the choropleth map, and the right shows the corresponding cartogram. Both images show the three longest rivers in England, and the color is mapped to CCG population. The target CCG is blinking on the choropleth (shown in black), participants are asked to identify this CCG on the cartogram.}
            \label{fig:task}
        \end{figure}
    }

>>>>

    {
        \begin{figure}[tb!]
            \centering
            \includegraphics[width=\columnwidth,keepaspectratio]{figure/evaluation/task.png}
            \caption{A sample location task for participants. The left shows the choropleth map, and the right shows the corresponding cartogram. Both images show the three longest rivers in England, and the color is mapped to CCG population. The target CCG is blinking on the choropleth (shown in black), participants are asked to identify this CCG on the cartogram. In this figure, $ \nodeErrCrossing $ is reduced from 9 to 0. }
            \label{fig:task}
        \end{figure}
    }

### 2023-03-23 paper/section/introduction.tex
draft: review 3

Cartograms are representations of geographical and abstract data based on a value-by-area mapping combining statistical and geographical information \cite{dent2009Cartography}. Various styles of cartograms have been proposed and implemented for applications such as urban planning \cite{harris2018Mapping, arranz-lopez2021Enduser}, natural hazard forecasting \cite{pappenberger2019Cartograms, park2020Flood}, conservation and environmental planning \cite{galluzzi2018Mapping, rocchini2019Cartogramming}, political and social demographics \cite{breitzman2018Using, alieva2021How}, and decision-making for public health \cite{gao2020Visualising, sack2021Visualizing}.

>>>>

Cartograms are representations of geographical and abstract data based on a value-by-area mapping combining statistical and geographical information \cite{dent2009Cartography,inoue2011New}. Various styles of cartograms have been proposed and implemented for applications such as urban planning \cite{harris2018Mapping, arranz-lopez2021Enduser}, natural hazard forecasting \cite{pappenberger2019Cartograms, park2020Flood}, conservation and environmental planning \cite{galluzzi2018Mapping, rocchini2019Cartogramming}, political and social demographics \cite{breitzman2018Using, alieva2021How}, and decision-making for public health \cite{gao2020Visualising, sack2021Visualizing}.

### 2023-03-23 paper/section/main.tex
draft: review 3

The overall algorithm terminates when the average node size $ \nodeSizeAvg $ reaches the max node size $ \nodeSizeMax $. At this point, the node layout is optimal where no node has crossed, or crossed by a river. Every node remains on the same side of the river as its centroid.

@@

{
\begin{figure*}[tb!]
    \centering
    \includegraphics[width=\textwidth,keepaspectratio]{figure/UI.png}
    \caption{A screenshot of the software. User options are provided to adjust the size, color mapping, visibility of nodes and rivers. Other options include the ability to control the overlap removal behavior: rivers can be static or dynamic. See \Cref{subsec:{User Options}} for more on user options.}
    \label{fig:overview}
\end{figure*}
}

>>>>

\new{There are two conditions that can terminate the algorithm. The first condition is when the average node size $ \nodeSizeAvg $ reaches the max node size, $ \nodeSizeMax $, set by the user. The second condition is when the displacement error, $ \nodeErrDisplacement $, reaches the max displacement error, $ \nodeErrDisplacementMax $ , allowed by the user.}

When the algorithm terminates, the node layout is considered optimal where no node has crossed, or crossed by a river \new{(denoted by $ \nodeErrCrossing $ = 0)}. Every node remains on the same side of the river as its centroid.

@@

\bobgraph{Error Metrics:} \new{The displacement error metric is used to evaluate the accuracy of the layout. The user can adjust the error threshold, which is used to terminate the algorithm.}

{
\begin{figure*}[tb!]
    \centering
    \includegraphics[width=\textwidth,keepaspectratio]{figure/UI.png}
    \caption{A screenshot of the software. User options are provided to adjust the terminating conditions (size and error), color mapping, visibility of nodes and rivers. Other options include the ability to control the overlap removal behavior: rivers can be static or dynamic. See \Cref{subsec:{User Options}} for more on user options. \new{In this figure, $ \nodeErrCrossing $ is reduced from 13 to 0, and $ \nodeErrDisplacement $ for X and Y axes are 59.5 and 56.56, respectively. }}
    \label{fig:overview}
\end{figure*}
}

### 2023-03-23 paper/section/related.tex
draft: review 3

One of the disadvantages of Dorling and Demers cartograms is legibility. The layout algorithms may displace regions far from their original position and make the maps more difficult to interpret. Our work extends Demers cartograms. We introduce a new type of topological feature, a river, aiming to improve the interpretation, readability, and geographical accuracy of this class of cartograms.

>>>>

One of the disadvantages of Dorling and Demers cartograms is legibility. The layout algorithms may displace regions far from their original position and make the maps more difficult to interpret. \new{\citea{nickel2022Multicriteria} present a method to compute stable Demers cartograms with multiple constraints to maintain adjacencies with zero overlapping nodes.}

In this paper, we introduce a new type of topological feature, a river, \new{as a constraint to compute the final layout}, aiming to improve the interpretation, readability, and geographical accuracy of this class of cartograms.
